\documentclass[12pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{xcolor}

\definecolor{accent}{RGB}{30,80,160}

\hypersetup{colorlinks=true, linkcolor=accent, urlcolor=accent}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{WanderSync} \textit{--- Task 1: Requirements \& Subsystems}}
\rhead{Team 15}
\rfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\begin{document}

\begin{center}
  {\LARGE\bfseries Task 1: Requirements and Subsystems}\\[0.4em]
  {\large WanderSync: Dynamic Itinerary, Disruption Management and Social Travel Hub}\\[0.2em]
  {\normalsize Team 15}
\end{center}

\vspace{1em}

% ================================================================
\section{Functional Requirements}
% ================================================================

The following functional requirements define the observable behaviours the WanderSync system must
provide. Each requirement is expressed as a user story and tagged with its architectural significance.

\subsection{FR1 --- User Authentication and Account Management}

\textit{As a traveller, I want to register with an email and password, log in, and maintain a personal
profile, so that my itineraries and preferences are securely associated with my account.}

\textbf{Architectural significance:} Drives stateless JWT-based session management and the separation
of the Authentication Service from domain logic. Establishes security boundaries respected by every
other subsystem.

\subsection{FR2 --- Unified Booking Aggregation}

\textit{As a traveller, I want to import booking confirmations from multiple providers (flights, hotels,
local transport) into a single normalised view, so that all travel details are accessible in one place.}

\textbf{Architectural significance:} Requires an Adapter layer per provider with a common
\texttt{BookingRecord} interface. Adding a new provider must touch no more than 2 files outside the
adapter module --- directly constraining the architecture towards low coupling and high cohesion.

\subsection{FR3 --- Chronological Itinerary Timeline}

\textit{As a traveller, I want to view all my bookings as a time-ordered timeline, so that I can
understand the sequence and gaps in my travel plan at a glance.}

\textbf{Architectural significance:} Requires the Itinerary Management Service to own an
authoritative, sorted view assembled from heterogeneous booking records. Timeline assembly is a
read-heavy, cacheable operation that informs the caching strategy.

\subsection{FR4 --- Real-Time Disruption Detection and Notification}

\textit{As a traveller, I want to be automatically notified when a disruption (flight delay,
cancellation, or severe weather) affects my itinerary, and to receive suggested alternatives, so
that I can re-plan with minimal effort.}

\textbf{Architectural significance:} This is the most architecturally significant requirement. It
mandates an Event-Driven Architecture in which the Disruption Detection Service subscribes to
external feeds via a message broker, processes events asynchronously, and publishes
\texttt{DisruptionEvent} messages consumed by the Notification and Itinerary services. This
decoupling is the primary driver of the chosen architectural style.

\subsection{FR5 --- Privacy-Preserving Social Travel Synchronisation}

\textit{As a traveller who opts in, I want to discover other users whose itineraries overlap with
mine in time and region, and to connect with them through a bilateral consent flow, so that I can
coordinate ride-shares or social activities while retaining control over my location data.}

\textbf{Architectural significance:} Requires geospatial indexing for efficient region-based
matching and a consent state machine (none $\to$ city-level $\to$ precise) that enforces the
privacy NFR at the data layer, not only the presentation layer.

\end{document}
